### 2013-12-29 docs/reports/finalreport/architecture.tex
revising finalreport - writing apply methods of aggregation functions

\section{System Architecture and Design}
The system is designed based on DDD (Data Driven Design) and Multi-Layer Architecture. As it is depicted in Figure \ref{fig:architecture}, the system is consisted of three main layers : Interface, Business and Data Access Layer. Data is passed between the layers using Model objects.

Interface layer can be divided into two main parts. Server side and client side. Server side which is denoted as Application Layer is following MVVC (Model-View, View, Controller) design model. It's main purpose is mapping Model View objects of Interface Layer to Model objects and passing them to Business Layer and vice verse. Client side web pages are designed based on MVVM (Model-View, View, Model) model. Tools used for applying the model are explained in the next section.

Using AOP (Aspect-Oriented Programming), logging, error handling and security system are designed on top of other layers.

>>>>

\section{Architecture and Design}
The system is designed based on DDD (Data Driven Design) and Multi-Layer Architecture. As it is depicted in Figure \ref{fig:architecture}, the system is consisted of three main layers : Interface, Business and Data Access Layer. Data is passed between the layers using Model objects.

Interface layer can be divided into two main parts. Server side and client side. Server side which is denoted as Application Layer is following MVVC (Model-View, View, Controller) design model. It's main purpose is mapping Model-View objects of Interface Layer to Model objects and passing them to Business Layer and vice verse. Client side web pages are designed based on MVVM (Model-View, View, Model) model. Tools used for applying the model are explained in Section\ref{sec:tools}.

Using AOP (Aspect-Oriented Programming), logging, error handling and security are designed on top of other layers.

### 2013-12-29 docs/reports/finalreport/design.tex
revising finalreport - writing apply methods of aggregation functions

\section{Tools and Technologies}
In this section, the main applied tools, technologies and libraries are briefly described following by their usage in the system.

\begin{itemize}
	\item \textbf{C\texttt{\#}.NET 4.5:} As the main programming language, the project is developing on C\texttt{\#}.NET 4.5 using Visual Studio 2013 IDE.
	\item \textbf{ASP.NET 4.5:} It provides the required framework for web programming. MVC.NET is used as the main server side platform.
	\item \textbf{MS SQL Azure:} As the system is deployed on Windows Azure platform, SQL Azure is selected as relational database.
	\item \textbf{Windows Azure:} Some special services like Cache, Storage and Service Bus are widely used in the project.
	\item \textbf{Lucene.NET:} The core of text processing, indexing and search is handled by Lucene. Lucene.NET is implemented by line to line translating from its Java version. While Lucene in Java provides more options, the .NET version is used to keep the integrity of project.
	\item \textbf{LINQToSQL:} Regarding to high integrity of the tool with MS SQL Server, it is used as ORM (Object-Relational Mapping).
	\item \textbf{HunAlign\cite{hunalign}:} It is light library which aligns bilingual text on the sentence level. Its input is tokenized and sentence-segmented text in two languages. In the simplest case, its output is a sequence of bilingual sentence pairs (bisentences). In the presence of a dictionary, hunalign uses it, combining this information  with Gale-Church sentence-length information. In the absence of a dictionary, it first falls back to sentence-length information, and then builds an automatic dictionary based on this alignment. Then it realigns the text in a second pass, using the automatic dictionary. The library is used for developing the translation memory in sentence level based on original and translated text.
	\item \textbf{KnockoutJS:} A JQuery-based library for applying MVVM pattern and associating between DOM and data model.
	\item \textbf{BreezeJS:} A handy JQuery-based library for declaring object models on client side and executing HTML Verbs integrated with ASP.NET MVC.
	\item \textbf{AutoMapper:} Widely used for mapping objects specially from object Models to object View Models.
	\item \textbf{AutoFac:} It is an IoC container for Microsoft .NET which manages the dependencies between classes.
	\item \textbf{SignalR:} It is a library for ASP.NET that makes it simple to add real-time web functionality. Using the library, we can easily have server-side code push content to the connected clients as it happens, in real-time. Chat and notification systems are developed using this library.
	\item \textbf{Postsharp:} It is an AOP framework for .NET. Most AOP implementation is based on the library.
\end{itemize}

>>>>

\section{Tools and Technologies}
\label{sec:tools}
In this section, the main applied tools, technologies and libraries are briefly described following by their usage in the system.

\begin{itemize}
	\item \textbf{C\texttt{\#}.NET 4.5:} As the main programming language, the project is being developed on C\texttt{\#}.NET 4.5 using Visual Studio 2013 IDE.
	\item \textbf{ASP.NET 4.5:} It provides the required framework for web programming. MVC.NET is used as the main server side platform.
	\item \textbf{MS SQL Azure:} As the system is deployed on Windows Azure platform, SQL Azure is selected as relational database.
	\item \textbf{Windows Azure:} Some special services like Cache, Storage and Service Bus are widely used in the project.
	\item \textbf{Lucene.NET:} The core of text processing, indexing and search is handled by Lucene. Lucene.NET is implemented by line to line translating from its Java version. While Lucene in Java provides more options, the .NET version is used to keep the integrity of project.
	\item \textbf{LINQToSQL:} Regarding to high integrity of the tool with MS SQL Server, LINQToSQL is used as ORM (Object-Relational Mapping) tool.
	\item \textbf{HunAlign\cite{hunalign}:} A light library which aligns bilingual text on the sentence level. Its input is tokenized and sentence-segmented text in two languages. In the simplest case, its output is a sequence of bilingual sentence pairs (bisentences). In the presence of a dictionary, hunalign uses it, combining this information  with Gale-Church sentence-length information. In the absence of a dictionary, it first falls back to sentence-length information, and then builds an automatic dictionary based on this alignment. Then it realigns the text in a second pass, using the automatic dictionary. The library is used for developing the translation memory in sentence level based on original and translated text.
	\item \textbf{KnockoutJS:} A JQuery-based library for applying MVVM pattern and associating between DOM and data model.
	\item \textbf{BreezeJS:} A handy JQuery-based library for declaring object models on client side and executing HTML Verbs integrated with ASP.NET MVC.
	\item \textbf{AutoMapper:} Widely used for mapping objects specially from Model objects to View-Model ones.
	\item \textbf{AutoFac:} An IoC container integrated for Microsoft .NET which manages the class dependencies.
	\item \textbf{SignalR:} A library for ASP.NET that makes it simple to add real-time web functionality. Using the library, we can easily have server-side code push content to the connected clients as it happens, in real-time. Chat and notification systems are developed using this library.
	\item \textbf{Postsharp:} An framework for developing AOP in .NET.
\end{itemize}

### 2013-12-29 docs/reports/finalreport/development.tex
revising finalreport - writing apply methods of aggregation functions

\section{System Development}
In this section, some special points related to development of different components are described.

\subsection{Order}
Ordering page is a full client-side page following the idea of SPA (Single Page Application) using KnockoutJS and BreezeJS. Complex business of the company for applying query, offering translators and purchasing order urges using design models and standards.
\subsection{Machine Learning's Data Accumulating}
In order to tackle the problem of translator's ranking, a data accumulating system is designed. Similar to Order, based on query document it offers three translators and stores client's choice. The data gathered by the system is used in a Machine Learning program using Learning to Rank algorithms in order to discover the underlying pattern for proposing the translators. The details of the project is described in Seminar lecture related to the project. In contrast to Order system, it eliminates translator's picture and name. It prevents bias in final answer by client (estimator) and puts emphasis on presented criteria.
\subsection{Text Matching}
Using Lucene translator's documents are stored based on their language. In order to achieve the final text matching value, the similarity between each document and query document is calculated. The problem here is the aggregation algorithm between the results. Finally, based on the results that are reported in Seminar lecture, GP2\cite{gp2} algorithm is implemented.
\subsection{Translation Memory}
As it's mentioned before, the aim of Translation Memory system is helping the translators to have an access to their previous-translated texts and applying them to their new translations. HunAlign is used to align the sentences of one text with the sentences of its corresponding text in another language. Although the library tends to be very error-prone specially for complex texts, adding dictionary and using rather simple texts lead to more reasonable results. At the end, Lucene is used for indexing and searching the sentences.

>>>>

\section{Development}
In this section, some special issues related to development of different components are described.

\subsection{Order}
Ordering page is a full client-side page following the idea of SPA (Single Page Application) using KnockoutJS and BreezeJS. Complex business of the company in applying query, offering translators and purchasing order urges using design models and standards.
\subsection{Machine Learning's Data Accumulating}
In order to tackle the problem of translator's ranking, a data accumulating system is designed. Similar to Order, based on query document it offers three translators and stores client's choice. The data gathered by the system is used in a Machine Learning program using Learning to Rank algorithms. It aims to discover the underlying pattern for proposing the translators. The details of the project is described in seminar lecture related to the project. In contrast to Order system, the system eliminates translator's picture and name which prevents bias in final answer by estimator and puts emphasis on the presented criteria.
\subsection{Text Matching}
Using Lucene, translator's documents are stored regarding to their languages. In order to achieve the final text matching value, the similarity between each document and query document is calculated. The main problem here is the way to  aggregate result scores. As the problem is addressed in Seminar lecture, GP2\cite{gp2} algorithm is implemented.
\subsection{Translation Memory}
As it's mentioned before, the aim of Translation Memory system is helping the translators to exploit their previous-translated texts in their new translations. In order to develop the system, first HunAlign library is used for aligning the sentences of one text with the sentences of its corresponding text in another language. Although the algorithm is very error-prone specially for complex texts, adding dictionary and using rather simple and straightforward texts lead to more reasonable results. At the end, Lucene indexes the text and provides searching abilities.

### 2013-12-29 docs/reports/finalreport/introduction.tex
revising finalreport - writing apply methods of aggregation functions

\section{Introduction}
As a hub for professional translation services, Nativy \cite{nativy}(founded 2011 in Vienna) offers its customers top-quality translations at reasonable terms.

The company works exclusively with qualified translators into their native language. All Nativy translations are reviewed in accordance with EN 15038, the European Quality Standard for Translation Services, and translators have to provide evidence of the required qualifications stipulated in the standard by means of their résumé.

By providing the platform, regardless to geographical location of translators and clients, they can communicate and proceed the translation process. It eases translating text to even not-so-popular languages and also reduces the final cost.

The features regarding to the internship has been developed since Summer 2013.

In the following, first we address the problem. Then in system architecture as well as design patterns and development techniques are explained. At the end related work to the project is briefly met.

>>>>

\section{Introduction}
As a hub for professional translation services, nativy \cite{nativy}(founded 2011 in Vienna) offers its customers top-quality translations at reasonable terms.

The company works exclusively with qualified translators into their native language. All nativy translations are reviewed in accordance with EN $15038$, the European Quality Standard for Translation Services, and translators have to provide evidence of the required qualifications stipulated in the standard by means of their résumé.

Using the platform, regardless to geographical location of translators and clients, they can communicate and proceed a translation process. It aims to ease translating text to even not-so-popular languages as well as reduction of final cost.

In the following, first I describe system requirements. Then system architecture and design are explained. Tools and Technologies applied in the platform are Section \ref{sec:tools}. At the end, some special issues during system development are reported in the last section.

### 2013-12-29 docs/reports/finalreport/problem.tex
revising finalreport - writing apply methods of aggregation functions

\section{Problem Statement}
The client uploads documents to the website and asks for translators in different languages. Based on four criteria, the system starts searching for the best three translators. These criteria are cost, delivery time, frequent cooperation and text matching. Every criterion has also its weight which defines the importance from client’s point of view.

Each translator is proposing a price for each language pair which is used for calculating final cost. Delivery time is calculated based on the schedule of translator. Finally, in order to find text matching value, the similarity between query document and previous translated documents is aggregated. In primitive steps of registration, every translator uploads the documents has been translated before. These documents are also considered for calculating the similarity.

After merging the results of different criteria, the system represents the most appropriate translators to the client. By choosing the translator and following payment process, the translation starts. After finishing translation, a qualified proof-reader chosen by client revises the text and may send some corrections to the translator. At the end the proof-reader rates the translation from different aspects.

The problems and requirements addressed in the project are as follows:
\begin{itemize}
	\item wizard-like page for ordering process in a SPA (Single Page Application) structure.
	\item Indexing previous-translated texts and finding an aggregation function for their similarity values with query document.
	\item Finding and tuning a ranking function for finding the best three translators among all.
	\item Calculating delivery time based on translator's schedule.
	\item Web API interface as well as web interface
	\item Payment process.
	\item Short response time.
	\item Considering different languages and timezones.
\end{itemize}

>>>>

\section{Requirements and Scenario}
In the first step, Translators define their profiles. Each translator is setting a price and duration per word for each language pair. Then, they upload the documents which has been translated before. These documents are used for calculating the similarity.

In order to search for a translator, the client uploads documents to the website. Based on four criteria, the system starts searching the best three translators. These criteria are cost, delivery time, frequent cooperation and text matching. Every criterion has also its weight which defines its importance from client's point of view.

Final cost is calculated based on price per word. Delivery time is estimated using the schedule of translator as well as duration per word. Finally, in order to find text matching value, the similarity between query document and previous translated documents is aggregated.

After merging the results of different criteria, the system represents the most appropriate translators to the client. By choosing the translator and following payment process, the translator is informed for starting translation. After finishing translation, a qualified proof-reader chosen by client revises the text and may send some corrections to the translator. At the end the proof-reader rates the translation.

The requirements considered in the project are as follows:
\begin{itemize}
	\item wizard-like page for ordering process in a SPA (Single Page Application) structure.
	\item Indexing previous-translated texts and finding an aggregation function for their similarity values regarding to query document.
	\item Developing a ranking function in order to find the best three translators among all.
	\item Calculating delivery time based on translator's schedule.
	\item Web as well as Web API interface.
	\item Payment process.
	\item Short response time.
	\item Considering different languages and timezones.
\end{itemize}

### 2013-12-29 docs/reports/finalreport/report.tex
revising finalreport - writing apply methods of aggregation functions

\maketitle
\begin{abstract}
The reports explains the efforts done by design and develop a translator
retrieval system. The system can be defined in domain of on-line translation. It aims to find an appropriate translator for a client and manages the process till the last step. Besides, by providing a translation memory system translators can apply their previous translated texts in their new ones. In the project, C\texttt{\#}.NET and MS SQL SERVER as main platform and Lucene.NET as text processor are used. It is designed based on DDD (Data Driven Design) model. Windows Azure is also selected as deployment environment.
\end{abstract}

>>>>

\maketitle
\begin{abstract}
The report explains the details of design and developing process of a translator retrieval platform. The platform can be defined in domain of on-line translation. It aims to suggest an appropriate translator to a client and manages the process of translation till the last step. Besides, by providing a translation memory system translators can exploit their previous translated texts in their new ones. C\texttt{\#}.NET and MS SQL SERVER as main platform and Lucene.NET as text processor are used. The system is designed based on DDD (Data Driven Design) model. Windows Azure is also selected as deployment environment.
\end{abstract}

### 2013-12-29 docs/seminar/evaluation.tex
revising finalreport - writing apply methods of aggregation functions

\subsection{Aggregation Functions}
TODO

>>>>

\subsection{Aggregation Functions}
Similar to \cite{agg-gp2}, outcome of three algorithms are compared. Top1 and Top5 are selected as two common forms TopN aggregation algorithm. TopN refers to algorithm that summarizes the N top documents (i.e. Top1 only using the top associated document to rank the candidates).

Feedbacks of Proof-readers after every translation are used as a basis for evaluating the algorithms. Since feedbacks are a measure for quality of translation, the more similar the ranking of algorithms to feedbacks are the better it is.

The results of applying Spearman correlation is shown in Table\ref{table:Spearman}. As the outcome shows, GP2 outperforms the other algorithms. In comparison to Top1, Top5 has slightly better performance. The results is also partly the same based on each language-pair.

\begin{table}
\begin{center}
\begin{tabular}{|c|c|c|c|}
\hline Algorithm & Top1 & Top5 & GP2  \\
\hline Spearman correlation & 0.049 & 0.076 & 0.14\\
\hline
\end{tabular}
\caption{Comparison between algorithms and feedbacks}
\label{table:Spearman}
\end{center}
\end{table}
